Updates on the Exoplanet Orbit Database

### 2014-01-01 draft/ms.tex
Refine structure and details, add outline for introduction.

% leading authors
\author{Eunkyu Han\altaffilmark{1,2}}
\author{Sharon X. Wang\altaffilmark{1,2,3}}
\author{Jason T. Wright\altaffilmark{1,2,3}}
\author{Ming Zhao\altaffilmark{1,2}}
\author{and Friends}

@@

The introduction Section...

@@

Restrict the updates in this section on EOD updates. We only report
new additions and revised fields here. For details on other fields,
see \cite{Wright2011}. We divide the fields into categories in
consistency with the interactive table on exoplanets.org. Some fields
are not explicitly included in the interactive table (e.g., the URLs), but are
explicitly listed in the downloadable {\tt .csv} file.\footnote{The
  entire dataset provided by exoplanets.org is available for download in a
  single CSV file at \url{http://exoplanets.org/csv-files/exoplanets.csv}}

@@

The fields XREF and XURL store the peer-reviewed reference and link to
the publication for the field X. The following fields now have XREF
and XURL: (previously in \citealt{Wright2011}) DIST, TRANSIT, BINARY;
(new) fields in stellar parameters: V\footnote{ZZZ VREF and VURL are
  also for J, H, KS. ZZZ}, VSINI, GAMMA; all orbit pars except for
trend and freeze\_ecc; all transit parameters; all SE parameters;
fields for stellar properties: MSTAR, RSTAR, TEFF, RHOSTAR, LOGG, FE.

@@

S - changed to SHK;

@@

We now include \kepler\ candidates...

We also include planets discovered microlensing, imaging, timing,
astrometric motion. Some microlensing and imaging planets are not
included in the EOD because of poorly characterized orbits...

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}\label{sec:conclusion}

@@

@@

SEDEPTHKS\dotfill & & Secondary eclipse depth in $K_{\rm S}$

@@

\tablenotetext{b}{XU, XUPPER, XLOWER, XREF, XURL etc.}

>>>>

% leading authors
\author{Eunkyu Han\altaffilmark{1,2}}
\author{Sharon X. Wang\altaffilmark{1,2,3}}
\author{Jason T. Wright\altaffilmark{1,2,3}}
\author{Ying Feng\altaffilmark{1,2}}
\author{Ming Zhao\altaffilmark{1,2}}
\author{Onsi Fakhouri}
\author{and Friends}

@@

Recent development of exoplanet discoveries, especially
\kepler\ discoveries.

The business of keeping track of exoplanet discoveries, where EOD
stands, and a brief history of EOD.

What this paper is about: an update on EOD and the services our
website, exoplanets.org, provide.

@@

Scope of EOD has changed in the following ways:

1. Definition of planets: not strictly smaller than 24 \mjup\ any
more? Or still true?

2. Host stars: not only `normal stars' any more?

3. Change on definition of `well-determined' orbital parameters?

4. Inclusion of planets discovered beyond RV and transit.

Purposes of EOD have not changed?

We only report new additions and revised fields here. For details on
other fields, see \cite{Wright2011}. We divide the fields into
categories in consistency with the interactive table on
exoplanets.org. Some fields are not explicitly included in the
interactive table (e.g., the URLs), but are explicitly listed in the
downloadable {\tt .csv} file.\footnote{The entire dataset provided by
  exoplanets.org is available for download in a single CSV file at
  \url{http://exoplanets.org/csv-files/exoplanets.csv}}

@@

The fields XREF and XURL store the peer-reviewed reference and link to
the publication for the field X. The following fields now have XREF
and XURL: (previously in \citealt{Wright2011}) DIST, TRANSIT, BINARY;
(new) fields in stellar parameters: V, VSINI, GAMMA; all orbit pars except for
trend and freeze\_ecc; all transit parameters; all SE parameters;
fields for stellar properties: MSTAR, RSTAR, TEFF, RHOSTAR, LOGG, FE.

@@

S - changed to SHK; What's the source for SHK and RHK? Still discovery
paper and Butler 2006?

@@

We now include \kepler\ candidates... They can be displayed by
checking the `Kepler' option for the interactive data table.

We also include robustly detected planets discovered microlensing,
imaging, timing, astrometric motion. They can be displayed by check
the `Other' option for the table. They are not included in the EOD
(especially some microlensing and imaging planets) because of poorly
characterized orbits...

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Updates on the Website}

Onsi? Essential updates on the website.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Future}\label{sec:conclusion}

Any planned future improvements and updates?

@@

NSF funding?

SXW acknowledges support from PSARC.

@@

SEDEPTHKS\dotfill & & Secondary eclipse depth in $K_S$

@@

\tablenotetext{b}{-UPPER etc. means ``-UPPER, -LOWER, U-, -REF, -URL",
where ``-" stands for the name of the field listed in the first
column. They are...}
